---
title: "Quantifying Virus Transmission Risk and Hygiene Intervention Effectiveness in Shared Office Environments"
format:
  html:
    code-tools: true
    code-overflow: wrap
    code-line-numbers: true
    embed-resources: true
editor: visual
code-annotations: hover
execute:
  warning: false
  message: false
---

**Authors:** Royani Saha^a^, Jonathan D. Sexton^a^, Ashton Norman^a^, Yang Zhan^a^, Amanda M. Wilson^a^, Sophie E. Upson^b^, Shweta Malik^b^, Carolyn Buckley^b^, Lisa M. Ackerley^b^, Stephanie Cooper^b^, Lucas Gent^b^, and Kelly A. Reynolds^a^

^a^ Department of Community, Environment & Policy, 1295 N. Martin Avenue, Mel and Enid Zuckerman College of Public Health, University of Arizona, Tucson, AZ, 85724 USA

^b^Reckitt Science and Innovation Center, Dansom Lane, Hull, East Riding of Yorkshire, HU8 7DS, United Kingdom

**GitHub Repository:** <https://github.com/esrac-research/office-hygiene-qmra>

## Set up

```{r}
#| code-fold: true
#| code-summary: "Show code - package loading"

#Install packman once in Console:
#install.packages("pacman")

pacman::p_load(
  tidyverse,
  scales, #percent function
  gt, 
  readxl,
  here,
  stats4,
  truncdist,
  triangle,
  fitdistrplus,
  ggplot2
)
```

```{r}
iterations <- 10000
set.seed(103050)
```

## Parameters

#### Surface Area & Pathogen Transfer Efficiency

```{r}

#hand-orifice contact areas
AHand <- runif(iterations, 445, 535)
AMouth <-runif(iterations, 1, 41) 
AEye <-runif(iterations, 0.1, 2) 
ANose <-runif(iterations, 0.1, 10) 


#pathogen transfer efficiency hand-to-orifice
TEorif_mean <- 0.339
TEorif_SD <- 0.1318

F23mean <- 0.339
F23SD <- 0.1318

F23<-rtrunc(iterations,"norm",a=0,b=1,mean=F23mean,sd=F23SD)
TEorif<-rtrunc(iterations,"norm",a=0,b=1,mean=TEorif_mean,sd=TEorif_SD)


```

#### Contact Frequencies

Hand-orifice contact rates were modeled using a hurdle approach to preserve the proportion of zero-contact trials. Nonzero contact rates were fit to lognormal distributions and capped at the 99th percentile to avoid unlikely upper-tail values.

```{r}
#| code-fold: true
#| code-summary: "Show code - contact data loading and distribution set up"
#| warning: false
#| message: false

contact_data <- na.omit(read_excel(here("Hotdesking_contact_data.xlsx")))

mouth <- contact_data$Mouth
mouth_nonzero <- mouth[mouth > 0]

eyes <- contact_data$Eyes
eyes_nonzero <- eyes[eyes > 0]

nose <- contact_data$Nose
nose_nonzero <- nose[nose>0]

#percent zeros for each orifice
percentzero_mouth <- length(mouth[mouth==0])/length(mouth)
percentzero_eyes <- length(eyes[eyes==0])/length(eyes)
percentzero_nose <- length(nose[nose==0])/length(nose)

#fit nonzeros to lognormal distribution (determined as best fit though separate testing)
fit_lnorm_mouth_nonzero <- fitdist(mouth_nonzero, "lnorm")
fit_lnorm_eyes_nonzero <- fitdist(eyes_nonzero, "lnorm")
fit_lnorm_nose_nonzero <- fitdist(nose_nonzero, "lnorm")
```

```{r}
#| code-fold: true
#| code-summary: "Show code - contact parameters"

#cap each non-zero distribution to 99th percentile
mouth_cap <- quantile(mouth_nonzero, 0.99)
eyes_cap  <- quantile(eyes_nonzero, 0.99)
nose_cap  <- quantile(nose_nonzero, 0.99)

#Hand-orifice contact rates per minute
HMouth <- ifelse(
  runif(iterations) < percentzero_mouth,
  0,
  rtrunc(
    iterations,
    "lnorm",
    a = 0,
    b = mouth_cap,
    meanlog = fit_lnorm_mouth_nonzero$estimate["meanlog"],
    sdlog   = fit_lnorm_mouth_nonzero$estimate["sdlog"]
  )
)

HEye <- ifelse(
  runif(iterations) < percentzero_eyes,
  0,
  rtrunc(
    iterations,
    "lnorm",
    a = 0,
    b = eyes_cap,
    meanlog = fit_lnorm_eyes_nonzero$estimate["meanlog"],
    sdlog   = fit_lnorm_eyes_nonzero$estimate["sdlog"]
  )
)


HNose <- ifelse(
  runif(iterations) < percentzero_nose,
  0,
  rtrunc(
    iterations,
    "lnorm",
    a = 0,
    b = nose_cap,
    meanlog = fit_lnorm_nose_nonzero$estimate["meanlog"],
    sdlog   = fit_lnorm_nose_nonzero$estimate["sdlog"]
  )
)

```

#### Pathogen Loading

Concentration on Person B's hands in each scenario

```{r}
#determined as LOD/n for scenario 4
LOD<-(5/3)

S1_Chand <- (rtriangle(iterations, a = 0, b = 300, c = 95))/AHand
S2_Chand <- (rtriangle(iterations, a = 25, b = 220, c = 75))/AHand
S3_Chand <- (rtriangle(iterations, a = 0, b = 20, c = 5))/AHand
S4_Chand <- (runif(iterations, min = 0, max = LOD))/AHand
S5_Chand <- (rtriangle(iterations, a = 0, b = 45, c = 30))/AHand
S6_Chand <- (rtriangle(iterations, a = 10, b = 26, c =25))/AHand
S4to6_Chand <- (rtriangle(iterations, a = 0, b = 45, c =10))/AHand

```

#### Transfer Rates & Dose Delivered (Cumulative)

Cumulative dose delivered to target membranes, dose time = 30 min

```{r}

DoseTime <- 30 #minutes

S1_RRota <- F23*S1_Chand*HMouth*AMouth*DoseTime
S2_RRota <- F23*S2_Chand*HMouth*AMouth*DoseTime
S3_RRota <- F23*S3_Chand*HMouth*AMouth*DoseTime
S4_RRota <- F23*S4_Chand*HMouth*AMouth*DoseTime
S5_RRota <- F23*S5_Chand*HMouth*AMouth*DoseTime
S6_RRota <- F23*S6_Chand*HMouth*AMouth*DoseTime
S4to6_RRota <- F23*S4to6_Chand*HMouth*AMouth*DoseTime

S1_RRhino <- F23*S1_Chand*((HMouth*AMouth)+(HEye*AEye)+(HNose*ANose))*DoseTime
S2_RRhino <- F23*S2_Chand*((HMouth*AMouth)+(HEye*AEye)+(HNose*ANose))*DoseTime
S3_RRhino <- F23*S3_Chand*((HMouth*AMouth)+(HEye*AEye)+(HNose*ANose))*DoseTime
S4_RRhino <- F23*S4_Chand*((HMouth*AMouth)+(HEye*AEye)+(HNose*ANose))*DoseTime
S5_RRhino <- F23*S5_Chand*((HMouth*AMouth)+(HEye*AEye)+(HNose*ANose))*DoseTime
S6_RRhino <- F23*S6_Chand*((HMouth*AMouth)+(HEye*AEye)+(HNose*ANose))*DoseTime
S4to6_RRhino <- F23*S4to6_Chand*((HMouth*AMouth)+(HEye*AEye)+(HNose*ANose))*DoseTime
```

#### Dose Response

```{r}

Rota_alpha <- 0.253
Rota_N50 <- 6.17

Rhino_alpha <- 0.221
Rhino_N50 <- 1.81
```

## Infection Probabilities

#### Rhinovirus

```{r}
#| code-fold: true
#| code-summary: "Show code"

S1_P_Rhino <- 1-((1+S1_RRhino*(2^(1/Rhino_alpha)-1)/Rhino_N50)^(-Rhino_alpha))
S2_P_Rhino <- 1-((1+S2_RRhino*(2^(1/Rhino_alpha)-1)/Rhino_N50)^(-Rhino_alpha))
S3_P_Rhino <- 1-((1+S3_RRhino*(2^(1/Rhino_alpha)-1)/Rhino_N50)^(-Rhino_alpha))
S4_P_Rhino <- 1-((1+S4_RRhino*(2^(1/Rhino_alpha)-1)/Rhino_N50)^(-Rhino_alpha))
S5_P_Rhino <- 1-((1+S5_RRhino*(2^(1/Rhino_alpha)-1)/Rhino_N50)^(-Rhino_alpha))
S6_P_Rhino <- 1-((1+S6_RRhino*(2^(1/Rhino_alpha)-1)/Rhino_N50)^(-Rhino_alpha))
S4to6_P_Rhino <- 1-((1+S4to6_RRhino*(2^(1/Rhino_alpha)-1)/Rhino_N50)^(-Rhino_alpha))

# Percent reductions in mean

S2_Rhino_percentreduction <- percent((mean(S1_P_Rhino)-mean(S2_P_Rhino))/mean(S1_P_Rhino), accuracy=0.01)

S3_Rhino_percentreduction <- percent((mean(S1_P_Rhino)-mean(S3_P_Rhino))/mean(S1_P_Rhino), accuracy=0.01)

S4_Rhino_percentreduction <- percent((mean(S1_P_Rhino)-mean(S4_P_Rhino))/mean(S1_P_Rhino), accuracy=0.01)

S5_Rhino_percentreduction <- percent((mean(S1_P_Rhino)-mean(S5_P_Rhino))/mean(S1_P_Rhino), accuracy=0.01)

S6_Rhino_percentreduction <- percent((mean(S1_P_Rhino)-mean(S6_P_Rhino))/mean(S1_P_Rhino), accuracy=0.01)

S4to6_Rhino_percentreduction <- percent((mean(S1_P_Rhino)-mean(S4to6_P_Rhino))/mean(S1_P_Rhino), accuracy=0.01)

```

```{r}
#| code-fold: true
#| code-summary: "Show code - table formatting"
#| 
rhinotable <-tibble::tibble(
  `Scenario`= c(
    "Scenario 1",
    "Scenario 2",
    "Scenario 3",
    "Scenario 4",
    "Scenario 5",
    "Scenario 6",
    "Scenarios 4-6"
    ),
  `Min` = c(
    min(S1_P_Rhino),
    min(S2_P_Rhino),
    min(S3_P_Rhino),
    min(S4_P_Rhino),
    min(S5_P_Rhino),
    min(S6_P_Rhino),
    min(S4to6_P_Rhino)
  ),
  `Median` = c(
    median(S1_P_Rhino),
    median(S2_P_Rhino),
    median(S3_P_Rhino),
    median(S4_P_Rhino),
    median(S5_P_Rhino),
    median(S6_P_Rhino),
    median(S4to6_P_Rhino)
  ),
  `Max` = c(
    max(S1_P_Rhino),
    max(S2_P_Rhino),
    max(S3_P_Rhino),
    max(S4_P_Rhino),
    max(S5_P_Rhino),
    max(S6_P_Rhino),
    max(S4to6_P_Rhino)
  ),
  `Mean` = c(
    mean(S1_P_Rhino),
    mean(S2_P_Rhino),
    mean(S3_P_Rhino),
    mean(S4_P_Rhino),
    mean(S5_P_Rhino),
    mean(S6_P_Rhino),
    mean(S4to6_P_Rhino)
  ),
  `Percent Reduction in Mean` = c(
    NA_real_,
    S2_Rhino_percentreduction,
    S3_Rhino_percentreduction,
    S4_Rhino_percentreduction,
    S5_Rhino_percentreduction,
    S6_Rhino_percentreduction,
    S4to6_Rhino_percentreduction
  )
)
  

rhinotable |>
  gt() |>
  tab_header(title = "Infection Probabilities and Risk Reductions for Rhinovirus (multiple orifices)") |>
  fmt_scientific(
    columns = c(`Min`, `Median`, `Max`, `Mean`),
    decimals = 2,
    exp_style = "E",
    force_sign_n = TRUE
  ) |>
  fmt_percent(
    columns = `Percent Reduction in Mean`,
    decimals = 2
  ) |>
  sub_missing(
    columns = everything(),  
    missing_text = ""
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) |>
  cols_label(`Percent Reduction in Mean`=html("Percent <br>Reduction <br>in Mean"))

```

#### Rotavirus

```{r}
#| code-fold: true
#| code-summary: "Show code"

S1_P_Rota <- 1-((1+S1_RRota*(2^(1/Rota_alpha)-1)/Rota_N50)^(-Rota_alpha))
S2_P_Rota <- 1-((1+S2_RRota*(2^(1/Rota_alpha)-1)/Rota_N50)^(-Rota_alpha))
S3_P_Rota <- 1-((1+S3_RRota*(2^(1/Rota_alpha)-1)/Rota_N50)^(-Rota_alpha))
S4_P_Rota <- 1-((1+S4_RRota*(2^(1/Rota_alpha)-1)/Rota_N50)^(-Rota_alpha))
S5_P_Rota <- 1-((1+S5_RRota*(2^(1/Rota_alpha)-1)/Rota_N50)^(-Rota_alpha))
S6_P_Rota <- 1-((1+S6_RRota*(2^(1/Rota_alpha)-1)/Rota_N50)^(-Rota_alpha))
S4to6_P_Rota <- 1-((1+S4to6_RRota*(2^(1/Rota_alpha)-1)/Rota_N50)^(-Rota_alpha))

# Percent reductions in mean

S2_Rota_percentreduction <- percent((mean(S1_P_Rota)-mean(S2_P_Rota))/mean(S1_P_Rota), accuracy=0.01)

S3_Rota_percentreduction <- percent((mean(S1_P_Rota)-mean(S3_P_Rota))/mean(S1_P_Rota), accuracy=0.01)

S4_Rota_percentreduction <- percent((mean(S1_P_Rota)-mean(S4_P_Rota))/mean(S1_P_Rota), accuracy=0.01)

S5_Rota_percentreduction <- percent((mean(S1_P_Rota)-mean(S5_P_Rota))/mean(S1_P_Rota), accuracy=0.01)

S6_Rota_percentreduction <- percent((mean(S1_P_Rota)-mean(S6_P_Rota))/mean(S1_P_Rota), accuracy=0.01)

S4to6_Rota_percentreduction <- percent((mean(S1_P_Rota)-mean(S4to6_P_Rota))/mean(S1_P_Rota), accuracy=0.01)

```

```{r}
#| code-fold: true
#| code-summary: "Show code - table formatting"

rotatable <-tibble::tibble(
  `Scenario`= c(
    "Scenario 1",
    "Scenario 2",
    "Scenario 3",
    "Scenario 4",
    "Scenario 5",
    "Scenario 6",
    "Scenarios 4-6"
    ),
  `Min` = c(
    min(S1_P_Rota),
    min(S2_P_Rota),
    min(S3_P_Rota),
    min(S4_P_Rota),
    min(S5_P_Rota),
    min(S6_P_Rota),
    min(S4to6_P_Rota)
  ),
  `Median` = c(
    median(S1_P_Rota),
    median(S2_P_Rota),
    median(S3_P_Rota),
    median(S4_P_Rota),
    median(S5_P_Rota),
    median(S6_P_Rota),
    median(S4to6_P_Rota)
  ),
  `Max` = c(
    max(S1_P_Rota),
    max(S2_P_Rota),
    max(S3_P_Rota),
    max(S4_P_Rota),
    max(S5_P_Rota),
    max(S6_P_Rota),
    max(S4to6_P_Rota)
  ),
  `Mean` = c(
    mean(S1_P_Rota),
    mean(S2_P_Rota),
    mean(S3_P_Rota),
    mean(S4_P_Rota),
    mean(S5_P_Rota),
    mean(S6_P_Rota),
    mean(S4to6_P_Rota)
  ),
  `Percent Reduction in Mean` = c(
    NA_real_,
    S2_Rota_percentreduction,
    S3_Rota_percentreduction,
    S4_Rota_percentreduction,
    S5_Rota_percentreduction,
    S6_Rota_percentreduction,
    S4to6_Rota_percentreduction
  )
)

rotatable |>
  gt() |>
  tab_header(title = "Infection Probabilities and Risk Reductions for Rotavirus (hand-to-mouth transmission)") |>
  fmt_scientific(
    columns = c(`Min`, `Median`, `Max`, `Mean`),
    decimals = 2,
    exp_style = "E",
    force_sign_n = TRUE
  ) |>
  fmt_percent(
    columns = `Percent Reduction in Mean`,
    decimals = 2
  ) |>
  sub_missing(
    columns = everything(),  
    missing_text = ""
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) |>
  cols_label(`Percent Reduction in Mean`=html("Percent <br>Reduction <br>in Mean"))

```

## Exposure Probabilities

Probability of at least one successful transfer event to a facial orifice during the modeled exposure period

P(exposure)=1−e\^RR

#### Rhinovirus

```{r}
#| code-fold: true
#| code-summary: "Show code"

S1_AllOrificesExp <- 1 - exp(-S1_RRhino)
S2_AllOrificesExp <- 1 - exp(-S2_RRhino)
S3_AllOrificesExp <- 1 - exp(-S3_RRhino)
S4_AllOrificesExp <- 1 - exp(-S4_RRhino)
S5_AllOrificesExp <- 1 - exp(-S5_RRhino)
S6_AllOrificesExp <- 1 - exp(-S6_RRhino)
S4to6_AllOrificesExp <- 1 - exp(-S4to6_RRhino)

# Percent reductions in mean

S2_Rhino_expreduction <- percent((mean(S1_AllOrificesExp)-mean(S2_AllOrificesExp))/mean(S1_AllOrificesExp), accuracy=0.01)

S3_Rhino_expreduction <- percent((mean(S1_AllOrificesExp)-mean(S3_AllOrificesExp))/mean(S1_AllOrificesExp), accuracy=0.01)

S4_Rhino_expreduction <- percent((mean(S1_AllOrificesExp)-mean(S4_AllOrificesExp))/mean(S1_AllOrificesExp), accuracy=0.01)

S5_Rhino_expreduction <- percent((mean(S1_AllOrificesExp)-mean(S5_AllOrificesExp))/mean(S1_AllOrificesExp), accuracy=0.01)

S6_Rhino_expreduction <- percent((mean(S1_AllOrificesExp)-mean(S6_AllOrificesExp))/mean(S1_AllOrificesExp), accuracy=0.01)

S4to6_Rhino_expreduction <- percent((mean(S1_AllOrificesExp)-mean(S4to6_AllOrificesExp))/mean(S1_AllOrificesExp), accuracy=0.01)


rhinoexptable <-tibble::tibble(
  `Scenario`= c(
    "Scenario 1",
    "Scenario 2",
    "Scenario 3",
    "Scenario 4",
    "Scenario 5",
    "Scenario 6",
    "Scenarios 4-6"
    ),
  `Min` = c(
    min(S1_AllOrificesExp),
    min(S2_AllOrificesExp),
    min(S3_AllOrificesExp),
    min(S4_AllOrificesExp),
    min(S5_AllOrificesExp),
    min(S6_AllOrificesExp),
    min(S4to6_AllOrificesExp)
  ),
  `Median` = c(
    median(S1_AllOrificesExp),
    median(S2_AllOrificesExp),
    median(S3_AllOrificesExp),
    median(S4_AllOrificesExp),
    median(S5_AllOrificesExp),
    median(S6_AllOrificesExp),
    median(S4to6_AllOrificesExp)
  ),
  `Max` = c(
    max(S1_AllOrificesExp),
    max(S2_AllOrificesExp),
    max(S3_AllOrificesExp),
    max(S4_AllOrificesExp),
    max(S5_AllOrificesExp),
    max(S6_AllOrificesExp),
    max(S4to6_AllOrificesExp)
  ),
  `Mean` = c(
    mean(S1_AllOrificesExp),
    mean(S2_AllOrificesExp),
    mean(S3_AllOrificesExp),
    mean(S4_AllOrificesExp),
    mean(S5_AllOrificesExp),
    mean(S6_AllOrificesExp),
    mean(S4to6_AllOrificesExp)
  ),
  `Percent Reduction in Mean` = c(
    NA_real_,
    S2_Rhino_expreduction,
    S3_Rhino_expreduction,
    S4_Rhino_expreduction,
    S5_Rhino_expreduction,
    S6_Rhino_expreduction,
    S4to6_Rhino_expreduction
  )
)
  

rhinoexptable |>
  gt() |>
  tab_header(title = "Exposure Probabilities for Rhinovirus (multiple orifices)") |>
  fmt_scientific(
    columns = c(`Min`, `Median`, `Max`, `Mean`),
    decimals = 2,
    exp_style = "E",
    force_sign_n = TRUE
  ) |>
  fmt_percent(
    columns = `Percent Reduction in Mean`,
    decimals = 2
  ) |>
  sub_missing(
    columns = everything(),  
    missing_text = ""
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) |>
  cols_label(`Percent Reduction in Mean`=html("Percent <br>Reduction <br>in Mean"))

```

#### Rotavirus

```{r}
#| code-fold: true
#| code-summary: "Show code"

S1_MouthExp <- 1 - exp(-S1_RRota)
S2_MouthExp <- 1 - exp(-S2_RRota)
S3_MouthExp <- 1 - exp(-S3_RRota)
S4_MouthExp <- 1 - exp(-S4_RRota)
S5_MouthExp <- 1 - exp(-S5_RRota)
S6_MouthExp <- 1 - exp(-S6_RRota)
S4to6_MouthExp <- 1 - exp(-S4to6_RRota)

# Percent reductions in mean

S2_Rota_expreduction <- percent((mean(S1_MouthExp)-mean(S2_MouthExp))/mean(S1_MouthExp), accuracy=0.01)

S3_Rota_expreduction <- percent((mean(S1_MouthExp)-mean(S3_MouthExp))/mean(S1_MouthExp), accuracy=0.01)

S4_Rota_expreduction <- percent((mean(S1_MouthExp)-mean(S4_MouthExp))/mean(S1_MouthExp), accuracy=0.01)

S5_Rota_expreduction <- percent((mean(S1_MouthExp)-mean(S5_MouthExp))/mean(S1_MouthExp), accuracy=0.01)

S6_Rota_expreduction <- percent((mean(S1_MouthExp)-mean(S6_MouthExp))/mean(S1_MouthExp), accuracy=0.01)

S4to6_Rota_expreduction <- percent((mean(S1_MouthExp)-mean(S4to6_MouthExp))/mean(S1_MouthExp), accuracy=0.01)


Rotaexptable <-tibble::tibble(
  `Scenario`= c(
    "Scenario 1",
    "Scenario 2",
    "Scenario 3",
    "Scenario 4",
    "Scenario 5",
    "Scenario 6",
    "Scenarios 4-6"
    ),
  `Min` = c(
    min(S1_MouthExp),
    min(S2_MouthExp),
    min(S3_MouthExp),
    min(S4_MouthExp),
    min(S5_MouthExp),
    min(S6_MouthExp),
    min(S4to6_MouthExp)
  ),
  `Median` = c(
    median(S1_MouthExp),
    median(S2_MouthExp),
    median(S3_MouthExp),
    median(S4_MouthExp),
    median(S5_MouthExp),
    median(S6_MouthExp),
    median(S4to6_MouthExp)
  ),
  `Max` = c(
    max(S1_MouthExp),
    max(S2_MouthExp),
    max(S3_MouthExp),
    max(S4_MouthExp),
    max(S5_MouthExp),
    max(S6_MouthExp),
    max(S4to6_MouthExp)
  ),
  `Mean` = c(
    mean(S1_MouthExp),
    mean(S2_MouthExp),
    mean(S3_MouthExp),
    mean(S4_MouthExp),
    mean(S5_MouthExp),
    mean(S6_MouthExp),
    mean(S4to6_MouthExp)
  ),
  `Percent Reduction in Mean` = c(
    NA_real_,
    S2_Rota_expreduction,
    S3_Rota_expreduction,
    S4_Rota_expreduction,
    S5_Rota_expreduction,
    S6_Rota_expreduction,
    S4to6_Rota_expreduction
  )
)
  

Rotaexptable |>
  gt() |>
  tab_header(title = "Exposure Probabilities for Rotavirus (hand-to-mouth transmission)") |>
  fmt_scientific(
    columns = c(`Min`, `Median`, `Max`, `Mean`),
    decimals = 2,
    exp_style = "E",
    force_sign_n = TRUE
  ) |>
  fmt_percent(
    columns = `Percent Reduction in Mean`,
    decimals = 2
  ) |>
  sub_missing(
    columns = everything(),  
    missing_text = ""
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) |>
  cols_label(`Percent Reduction in Mean`=html("Percent <br>Reduction <br>in Mean"))

```

```{r}
#| code-fold: true
#| code-summary: "Show code - plot formatting"
#| 
infection_long <- bind_rows(
  tibble(Pathogen = "Rhinovirus", Scenario = "S1\nBaseline", Probability = S1_P_Rhino),
  tibble(Pathogen = "Rhinovirus", Scenario = "S2\nContract", Probability = S2_P_Rhino),
  tibble(Pathogen = "Rhinovirus", Scenario = "S3\nTargeted\nHygiene", Probability = S3_P_Rhino),
  tibble(Pathogen = "Rhinovirus", Scenario = "S4\nDisinfection\n+ nudges", Probability = S4_P_Rhino),
  tibble(Pathogen = "Rhinovirus", Scenario = "S5\nHand\nhygiene", Probability = S5_P_Rhino),
  tibble(Pathogen = "Rhinovirus", Scenario = "S6\nSurface + hand\nhygiene", Probability = S6_P_Rhino),
  tibble(Pathogen = "Rhinovirus", Scenario = "S4-6\nCombined", Probability = S4to6_P_Rhino),
  
  tibble(Pathogen = "Rotavirus", Scenario = "S1\nBaseline", Probability = S1_P_Rota),
  tibble(Pathogen = "Rotavirus", Scenario = "S2\nContract", Probability = S2_P_Rota),
  tibble(Pathogen = "Rotavirus", Scenario = "S3\nTargeted\nHygiene", Probability = S3_P_Rota),
  tibble(Pathogen = "Rotavirus", Scenario = "S4\nDisinfection\n+ nudges", Probability = S4_P_Rota),
  tibble(Pathogen = "Rotavirus", Scenario = "S5\nHand\nhygiene", Probability = S5_P_Rota),
  tibble(Pathogen = "Rotavirus", Scenario = "S6\nSurface + hand\nhygiene", Probability = S6_P_Rota),
  tibble(Pathogen = "Rotavirus", Scenario = "S4-6\nCombined", Probability = S4to6_P_Rota)
)

infection_long$Scenario <- factor(
  infection_long$Scenario,
  levels = c("S1\nBaseline", "S2\nContract", "S3\nTargeted\nHygiene",
             "S4\nDisinfection\n+ nudges", "S5\nHand\nhygiene",
             "S6\nSurface + hand\nhygiene", "S4-6\nCombined")
)

ggplot(infection_long, aes(x = Scenario, y = Probability, fill = Pathogen)) +
  geom_boxplot(
    width = 0.65,
    outlier.alpha = 0.15,
    alpha = 0.75
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 21,
    size = 2.6,
    fill = "white",
    color = "black",
    position = position_dodge(width = 0.75)
  ) +
  facet_wrap(~Pathogen, ncol = 1) +
  scale_y_continuous(
    labels = scientific,
    limits = c(0, NA)
  ) +
  scale_fill_manual(values = c(
    "Rhinovirus" = "#0c234b",
    "Rotavirus" = "#6baed6"
  )) +
  labs(
    title = "Estimated Infection Risk by Intervention Scenario",
    x = NULL,
    y = "Probability of infection"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 35, hjust = 1),
    panel.grid.minor = element_blank()
  )
```

```{r}
#| code-fold: true
#| code-summary: "Show code - plot formatting"

infection_summary <- infection_long |>
  group_by(Pathogen, Scenario) |>
  summarise(
    mean = mean(Probability),
    lower = quantile(Probability, 0.025),
    upper = quantile(Probability, 0.975),
    .groups = "drop"
  )

ggplot(infection_summary, aes(x = Scenario, y = mean, color = Pathogen)) +
  geom_pointrange(
    aes(ymin = lower, ymax = upper),
    size = 0.6,
    linewidth = 0.8
  ) +
  facet_wrap(~Pathogen, ncol = 1) +
  scale_y_continuous(
    labels = scientific,
    limits = c(0, NA)
  ) +
  scale_color_manual(values = c(
    "Rhinovirus" = "#0c234b",
    "Rotavirus" = "#6baed6"
  )) +
  labs(
    title = "Estimated Infection Risk by Intervention Scenario",
    x = NULL,
    y = "Mean probability with 95% simulation interval"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 35, hjust = 1),
    panel.grid.minor = element_blank()
  )
```
